---
title: "Flying, Sports, Thanksgiving Project Proposal for Fruity Pebbles lab 11L"
subtitle: ""
author: "Fruity Pebbles 11L - Catherine Liu, Navya Belavadi, Mahish Kewalramani"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA, 
                      message = FALSE, warning = FALSE,
                      fig.height = 6, fig.width = 9, fig.align = "center")
```

```{r load_packages}
library(tidyverse)
library(haven)
```

```{r load_data}
sports_donations <- read.csv("Data/sports-political-donations.csv")

flying <- read.csv("Data/flying-etiquette.csv")

thanksgiving <- read.csv("Data/thanksgiving-2015-poll-data.csv")
```
## Data Set #1: Flying Etiquiette
This data was collected through a SurveyMonkey poll in August of 2014. Some 
of the relevant variables include age and height of the flier, whether they 
recline their seat and other opinions on the action like whether they would
eliminate it outright or the rudeness of it, and their perspective on whether 
a certain set of actions is rude to do on a plane or not. Another replant 
variable is whether the flier has kids under the age of 18. Our research topic 
looks into the relationship between the age of a flier and and if they have kids
under 18, and whether or not they think it is rude to bring unruly children on a
plane. What impact does age of a flier and whether or not they have children 
under 18 have on their opinion on whether it is rude to knowingly bring unruly 
children on a flight. An older flier with kids under 18 is more likely to think 
it is not rude to knowingly bring unruly children on a plane than younger fliers
without kids or with kids above the age of 18.

## Data Set #2: Sports Political Donations
This data comes from the story "Inside The Political Donation History Of Wealthy
Sports Owners", and contains every confirmed donation from all sports owners 
from 2016 onwards. Some relevant variables includes the league that the money is
coming from, the sport that the money is coming from, who the money is coming 
from, where the money is going to (as in which party), what years election the 
money is going to, and how much money is being donated. Our research topic will 
look into which leagues donate the most to which party and how the money has 
changed between election years (2016, 2018, 2020). This will be done through 
hypothesis testing and just general viewing of all the data. How has the amount 
of money being donated to political campaigns changed across the three election 
cycles for each individual sport? Given that sports stars influence in politics 
has grown over the years (E.x. Kapernick, BLM movement in sports) I think that
the amount of money will have definitely increased between 2016 and 2020. The 
2018 cycle will have less donations because it is not a presidential election.

## Data Set #3: Thanksgiving
This is the data behind the story "Here's What Your Part of America Eats On 
Thanksgiving," which was gathered using a Survey Monkey poll from Nov 17, 2015. 
Variables range from what is served for each dish (main, side, stuffing,
sauce, etc), and various other common American thanksgiving traditions. Other 
relevant variables included age, gender, household income, and US region. 
Our research topic will examine the link between household income with Black
Friday shopping habits in each categorical region (Urban, Suburban, Rural). 
How does the total combined income that all members of ones household earned in 
the past year impact whether or not an individual will go Black Friday shopping
on Thanksgiving in each region -- Urban, Suburban, or Rural?
Our guess is that as household income increases to a certain extent, an 
individual is more likely to go Black Friday shopping on Thanksgiving, with the 
exception being that extremely wealthy are less likely to go. And, as you 
observe from rural to suburban to urban, we predict that the likelihood of a 
resident going Black Friday shopping will increase. The reasoning is that as 
household income increases, that individual will most likely have the means to 
go Black Friday shopping, but we also take into consideration that the top 
ranked household income people might not require sales to purchase. 
Geographically speaking, there should be more stores in urban areas than rural 
and suburban areas so the increase we predicted should make sense.  
