---
title: "Who is Leaving Thanksgiving Dinner to Go Black Friday Shopping?"
subtitle: "Date: 04-28-2021"
author: "FruityPebbles 11L - Mahish Kewalramani, Catherine Liu, Navya Belavadi"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA, 
                      message = FALSE, warning = FALSE,
                      fig.height = 6, fig.width = 9, fig.align = "center")
```

```{r echo=TRUE}
library(tidyverse)
library(broom)
library(performance)
library(see)
library(scales)
```
# Introduction
Our data set, thanksgiving-2015-poll-data.csv, is the data behind the story 
“Here’s What Your Part of America Eats On Thanksgiving," (https://fivethirtyeight.com/features/heres-what-your-part-of-america-eats-on-thanksgiving/) 
which was gathered using a Survey Monkey poll from Nov 17, 2015. 1,058 
respondents answered questions about their thanksgiving habits and traditions.
We were especially interested in the variable in which the respondent reported 
whether they would go Black Friday shopping on Thanksgiving day or not. We 
decided to explore the other factors that could contribute to this variable, 
wondering if it could reveal anything about American values of consumerism over 
family time or what goes into  deciding whether an individual will leave 
Thanksgiving dinner for sales.

**Research Question:** Is there a relationship between household 
income, gender, age, and categorical region with the likelihood that an 
individual will go Black Friday shopping on Thanksgiving (shop early)?

**Hypotheses:** As household income increases to a certain extent, an 
individual will be more likely to go Black Friday shopping on Thanksgiving,
with the exception being that extremely wealthy are less likely to go. As age 
increases, early Black Friday shoppers should decrease. We predict that 
women will be more likely to shop early. And, as we observe from rural to 
suburban to urban, we predict that the likelihood of a resident going Black 
Friday shopping will increase.

For further research, we looked to these articles:
https://money.cnn.com/2015/11/30/news/companies/cyber-monday-sales/
https://news.gallup.com/poll/158927/black-friday-shopping-mostly-young.aspx

**Relevant Variables:**

**income:** the household income range, we binned into 4 categories (0 to 
24,999, 25,000 to 74,999, 75,000 to 99,999, and 100,000+)

**gender:** male or female 

**age:** age in years, responses were binned into 4 categories (18-29, 30-44, 
45-59, 60+)

**location_type:** describes the region as Urban, Rural, or Suburban 

**black_friday:** 1 if the individual responded "yes" to the question "Will you
shop any Black Friday sales on Thanksgiving day," and 0 if the individual 
responded "no." This is the variable that we are testing to see how it is
impacted by the above 4 variables.

*Data manipulation:*
Before working with our data, we manipulated it by renaming variables to more 
concise names, changing blank responses to N/A to filter them out, and changing 
yes and no in the black_friday variable to 1 and 0 so it would be easier to do 
the regression model. 

# Methodology

**Statistical Method:**
We decided to use logistic regression because our response of interest, whether
an individual will go Black Friday shopping on Thanksgiving, is categorical and 
binary, with the responses being either "yes" or "no." We will use this logistic 
regression model to obtain predicted probabilities of success for our binary 
response variable, going Black Friday shopping early. To find the our logistic 
regression model with the best fit, we will look at the p-values for different 
variables and eliminate ones that are not significant. By doing so, we will end 
with a logistic regression model that ideally is the most suitable for 
predicting Black Friday shopping.

```{r load_clean_data, echo = FALSE}
thanksgiving <- read.csv("Data/thanksgiving-2015-poll-data.csv")

thanksgiving <- thanksgiving %>% 
  select(
    How.much.total.combined.money.did.all.members.of.your.HOUSEHOLD.earn.last.year., 
    What.is.your.gender., 
    Age, How.would.you.describe.where.you.live., 
    Will.you.shop.any.Black.Friday.sales.on.Thanksgiving.Day., 
    Will.you.employer.make.you.work.on.Black.Friday.) %>% 
  mutate(
    income = How.much.total.combined.money.did.all.members.of.your.HOUSEHOLD.earn.last.year., 
    gender = What.is.your.gender., age = Age, 
    location_type = How.would.you.describe.where.you.live., 
    black_friday = Will.you.shop.any.Black.Friday.sales.on.Thanksgiving.Day., 
    work = Will.you.employer.make.you.work.on.Black.Friday.) %>% 
  select(income, gender, age, location_type, black_friday, work) %>% 
  filter(income != "Prefer not to answer")

thanksgiving$income[thanksgiving$income == ""]  <- NA
thanksgiving$gender[thanksgiving$gender == ""]  <- NA
thanksgiving$age[thanksgiving$age == ""]  <- NA
thanksgiving$location_type[thanksgiving$location_type == ""]  <- NA
thanksgiving$black_friday[thanksgiving$black_friday == ""]  <- NA
thanksgiving$work[thanksgiving$work == ""]  <- NA

thanksgiving <- thanksgiving %>% 
  filter(!is.na(black_friday))

thanksgiving$black_friday <- factor(thanksgiving$black_friday,
                                    levels = c("No", "Yes"),
                                    labels = c(0,1))

```

## Exploratory Data Analysis

*Visualization Method:*
For these first few graphs, we decided to use grouped and percent stacked 
bar charts (varying between the two based on how many groups were included for 
easier readability). After experimenting with other graphs, we felt this was the 
best way for a reader to quickly spot the relationships without unnecessary 
complications.

#### Income vs. Black Friday Shopping:

First we are going to observe the different percentages within the income groups
that the data provides of people that either will or will not go Black Friday 
shopping early.

```{r incomes, fig.width = 6, fig.height = 4, echo = FALSE}
incomes <- thanksgiving %>%
  mutate(income = factor(income, levels = c(
    "$0 to $9,999", "$10,000 to $24,999","$25,000 to $49,999",
    "$50,000 to $74,999", "$75,000 to $99,999", "$100,000 to $124,999", 
    "$125,000 to $149,999","$150,000 to $174,999","$175,000 to $199,999", 
    "$200,000 and up"))) %>% 
  filter(!is.na(income)) %>% 
  group_by(income) %>%
  count(black_friday) %>% 
  mutate(perc = n/sum(n)) 
  
incomes %>%
  mutate(Shopping = if_else(black_friday == 1, "Yes", "No")) %>%
  ggplot(aes(income, perc)) +
  geom_bar(aes(fill = Shopping), position = "fill", stat="identity") +
  labs(title = "Income Effect on Thanksgiving Shopping", x= "Household
       Income", y = "Percentage") +
  coord_flip() + scale_y_continuous(labels = 
      percent)
```

From this initial visualization of the relationship between Household Income 
and whether or not an individual will go Black Friday shopping early, we 
decided to bin the income variable further into less categories.
We chose the bins of a household income from $0 to $24,999, $25,000 to 
$74,999, $75,000 to $99,999, and $100,000+ because it appeared that the 
percentages naturally divide across those intervals.

```{r incomes_binned, fig.width = 6, fig.height = 4, echo = FALSE}
binned_incomes <- thanksgiving %>% 
  mutate(income = case_when(income == '$0 to $9,999' ~ '$0 to $24,999',
                            income == "$10,000 to $24,999"~'$0 to $24,999',
                            income == "$25,000 to $49,999"~
                            '$25,000 to $74,999',  
                            income == "$50,000 to $74,999" ~
                              '$25,000 to $74,999', 
                            income == "$75,000 to $99,999" ~
                              "$75,000 to $99,999",
                            income == "$100,000 to $124,999" ~
                              '$100,000+',
                            income == "$125,000 to $149,999" ~ 
                              '$100,000+',
                            income == "$150,000 to $174,999" ~
                              '$100,000+',
                            income == "$175,000 to $199,999" ~
                              '$100,000+',
                            income == "$175,000 to $199,999" ~
                              "$100,000+")) %>% 
  mutate(income = factor(income, levels = c('$0 to $24,999',
                                            '$25,000 to $74,999',
                                            "$75,000 to $99,999",
                                            '$100,000+')))
binned_incomes %>% 
  filter(!is.na(income)) %>% 
  group_by(income) %>%
  count(black_friday) %>% 
  mutate(perc = n/sum(n)) %>% 
  mutate(Shopping = if_else(black_friday == 1, "Yes", "No")) %>%
  ggplot(aes(income, perc)) +
  geom_bar(aes(fill = Shopping), position = "dodge", stat="identity") +
  labs(title = "Binned Income Effect on Thanksgiving Shopping", x= 
         "Household Income", y = "Percentage") +
  coord_flip() + scale_y_continuous(labels = percent)
```

From our visualization, it appears that there is a clear relationship between 
household income and probability of going Black Friday shopping early -- as 
household income increases, the percentage of people that will go Black Friday 
shopping decreases. The highest percentage of individuals that went shopping, at 
around 35%, belongs to those in the $0 to $24,999 income bracket, whereas the 
lowest percentage of individuals that went shopping, at roughly 18%, refers to 
the wealthiest income bracket ($100,000+).

#### Gender vs. Black Friday Shopping: 

Next we will visualize the percentages within gender to see whether gender 
affects the likelihood. We ask the question, will a greater percentage of males 
or females go Black Friday shopping on Thanksgiving?

```{r gender, fig.width = 5, fig.height = 3, echo = FALSE}
gen <- thanksgiving %>% 
  filter(gender != "NA") %>% 
  group_by(gender, black_friday) %>% 
  count() %>% 
  group_by(gender) %>% 
  mutate(pct = n/sum(n))

gen %>%
  mutate(Shopping = if_else(black_friday == 1, "Yes", "No")) %>%
  ggplot(aes(gender, pct)) +
  geom_bar(aes(fill = Shopping), position = "dodge", stat="identity") +
  labs(title = "Gender Effect on Thanksgiving Shopping", x= "Gender", y = 
         "Percentage") + scale_y_continuous(labels = percent)
```

It appears that from this plot, the percentage within males and females that 
will or will not go Black Friday shopping early is pretty similar, with female 
likelihood of shopping only being slightly higher than that of males (less than 
5% greater).

#### Location Type vs. Black Friday Shopping:

Next will visualize the effect of the type of location on Black Friday shopping. 
The three location types we have from the data set are rural, 
suburban, and urban.

```{r location, fig.width = 5, fig.height = 3, echo = FALSE}
loc <- thanksgiving %>% 
  filter(location_type != "NA") %>% 
  group_by(location_type, black_friday) %>% 
  count() %>% 
  group_by(location_type) %>% 
  mutate(pct = n/sum(n))

loc %>%
  mutate(Shopping = if_else(black_friday == 1, "Yes", "No")) %>%
  ggplot(aes(location_type, pct)) +
  geom_bar(aes(fill = Shopping), position = "dodge", stat="identity") +
  labs(title = "Location Type Effect on Thanksgiving Shopping", x= 
         "Location Type", y = "Percentage") + scale_y_continuous(labels = 
          percent)
```

From our visualization, the percentage of individuals who will go Black 
Friday shopping across different location types does not seem to vary
significantly. However, the individuals with the greatest percentage saying yes 
to going shopping on Thanksgiving live in Urban areas, followed by Rural and 
Suburban. 

#### Age vs. Black Friday Shopping:

Finally, we will visualize the percentage of Black Friday shoppers across
different age groups of the survey respondents (18-29, 30-44, 45-59, and 60+).

```{r age_exploration, fig.width = 5, fig.height = 3, echo = FALSE}
ages <- thanksgiving %>% 
  filter(age != "NA") %>% 
  group_by(age, black_friday) %>% 
  count() %>% 
  group_by(age) %>% 
  mutate(pct = n/sum(n))

ages %>%
  mutate(Shopping = if_else(black_friday == 1, "Yes", "No")) %>%
  ggplot(aes(age, pct)) +
  geom_bar(aes(fill = Shopping), position = "dodge", stat="identity") +
  labs(title = "Age Effect on Thanksgiving Shopping", x= "Age", y = 
         "Percentage") + scale_y_continuous(labels = 
      percent)
```

From this visualization, we can observe that within older age groups, there
is a lower percentage of people who report that they will go Black Friday
shopping early. The age group 18 to 29 years old has the highest percentage
of individuals who will go Black Friday shopping, while the group 60+ has
the lowest. Overall, there is a clear relationship that as age increases, the 
likelihood of an individual Black Friday shopping early decreases. 

## Logistic Regression Model

We will start out with a logistic regression model that includes all 
the potentially interesting variables that could contribute to
Black Friday Shopping early. For our first logistic regression model, we 
assigned Black Friday shopping as the response variable and income, gender, 
location type, and age as the explanatory variables.

```{r log_mod, fig.width = 6, fig.height = 4, echo = FALSE}
log_mod_1 <- binned_incomes %>% 
  mutate(income = factor(income, levels = c('$0 to $24,999',
                                            '$25,000 to $74,999', 
                                            "$75,000 to $99,999",
                                            '$100,000+'))) %>% 
  glm(black_friday ~ income + gender + location_type + age, 
               data = ., family = "binomial")

tidy(log_mod_1)
```

**Elimination of Variables:**

Here we are removing gender as a variable, because it has a really high 
p-value and therefore seems not to have a very large effect on Black Friday 
Shopping. For this next logistic regression model, we have income, location 
type, and age as the explanatory variables.

```{r first_elimination, fig.width = 6, fig.height = 4, echo = FALSE}
log_mod_2 <- binned_incomes %>% 
  mutate(income = factor(income, levels = c('$0 to $24,999',
                                            '$25,000 to $74,999', 
                                            "$75,000 to $99,999",
                                            '$100,000+'))) %>% 
  glm(black_friday ~ income + location_type + age, 
               data = ., family = "binomial")

tidy(log_mod_2)
```

Next, we found that since location type has the next highest p-value,
we should try eliminating that as well. For this final logistic 
regression model, we have income and age as the only explanatory variables since
those had the lowest p values and therefore greatest impact on shopping. 

```{r second_elimination, fig.width = 6, fig.height = 4, echo = FALSE}
log_mod_3 <- binned_incomes %>% 
  mutate(income = factor(income, levels = c('$0 to $24,999',
                                            '$25,000 to $74,999', 
                                            "$75,000 to $99,999",
                                            '$100,000+'))) %>% 
  glm(black_friday ~ income + age, 
               data = ., family = "binomial")

tidy(log_mod_3)
```

**Model Performance:**

We decided to analyze the performance of our 3 logistic models by looking
at the Bayesian Information Criterion(BIC) because it takes into account
both model performance and model complexity. For comparing models, the smaller 
the BIC score, the better the fit is.

*Logistic Regression Model 1 Performance:*
```{r mod_perf1, echo = FALSE}
model_performance(log_mod_1)
```
*Logistic Regression Model 2 Performance:*
```{r mod_perf2, echo = FALSE}
model_performance(log_mod_2)
```
*Logistic Regression Model 3 Performance:*
```{r mod_perf3, echo = FALSE}
model_performance(log_mod_3)
```

From looking at the respective BIC for our 3 models, we decided to select
our third model. The BIC statistic, 841.098, is the lowest out of the three, 
and therefore we can assume that it is has the best performance, while not 
being overly complicated. In our case, BIC proved to be the best measure of 
model fit to use because it actually appropriate for our logistic regression 
models and it adjusts for both model performance and complexity.

**Binned Residuals Plot:**

After deciding that our third model was the most suitable in predicting early
Black Friday shoppers, we decided to make a Binned Residuals plot to assess the 
fit of the model further. The plot is created by dividing the data into 
bins based on their fitted values, and then plotting the average residual 
versus the average fitted value for each bin. If the model is true, we 
expect 95% of the residuals to fall inside the error bounds.

```{r binned_residuals, fig.width = 5, fig.height = 3, echo = FALSE}
binned_residuals(log_mod_3) 
```

Because 100% of our residuals are inside the error bounds, we can confirm
that this model is a good fit. 

### Predicted Probabilities:

Finally, we decided to make a predicted probabilities plot to show the effect
of age and income on Black Friday shopping early.

```{r predicted_probabilities, echo = FALSE}
tibble(
  income = rep(c('$0 to $24,999','$25,000 to $74,999', 
                 "$75,000 to $99,999","$100,000+"), each = 4),
  age = rep(c("18 - 29", "30 - 44","45 - 59","60+"), times = 4)) %>% 
  mutate(income = factor(income, levels = c('$0 to $24,999',
                                            '$25,000 to $74,999', 
                                            "$75,000 to $99,999",
                                            '$100,000+'))) %>% 
  augment(log_mod_3, newdata = .) %>% 
  mutate(predicted_p = exp(.fitted) / (1 + exp(.fitted))) %>% 
  ggplot(aes(x = income, y = predicted_p, color = age)) +
  geom_point(size = 2.8) +
  theme_minimal(base_size = 12) +
  labs(title = "Predicted Probability of Black Friday Shopping Based on 
       Household Income", 
       x = "Household Income", y = "Predicted P", color = "Age")

```

# Results
After our data analysis, we concluded that there is a significant relationship
between household income and age in whether an individual will go 
Black Friday shopping on Thanksgiving. While there was a slightly greater 
percentage of females than males going shopping early and the greatest 
percentage of individuals shopping early were from an Urban area (by a very
small margin), gender and location type had little to no impact in comparison to
household income and age. We found that the predicted probability of going Black
Friday shopping early decreases with a higher household income and age. 

**Main results**
From our analysis we obtained the logistic regression model:

$$\text{log}\left(\frac{\hat{p}}{1-\hat{p}}\right) = -0.342 -
0.234~(income25,000to74,999) - 0.472~(income75,000to99,999) - 
0.719~(income100,000+) - $$
$$0.161~(age30-44) - 0.606~(age45 - 59) - 1.054~(age60+)$$
We can configure the model to get a model for $\hat{p}$ is the probability that 
some event occurs with our event being that an individual will shop.

$$\hat{p} = \frac{e^{-0.342 - 
0.234~(income25,000to74,999) - 0.472~(income75,000to99,999) - 
0.719~(income100,000+) - }}{{1+e^{-0.342 - 
0.234~(income25,000to74,999) - 0.472~(income75,000to99,999)- 
0.719~(income100,000+)
- }}}$$
$$\frac{^{0.161~(age30-44) - 0.606~(age45 - 59) - 
1.054~(age60+)}}{^{0.161~(age30-44) - 0.606~(age45 - 59) - 1.054~(age60+)}}$$

We can also put our interpretation in odds to determine 
$\frac{\hat{p}}{1-\hat{p}}$,the odds that the event occurs. 

$$\frac{\hat{p}}{1-\hat{p}}= e^{-0.342 - 0.234~(income25,000to74,999) - 
0.472~(income75,000to99,999) - 0.719~(income100,000+)- }$$
$$^{0.161~(age30-44) - 0.606~(age45 - 59) - 1.054~(age60+)}$$
Our intercept of -0.342 can be interpreted as the log-odds of Black Friday 
shopping for an individual who is 18 to 29 years old and in the 
$0 to 24,999 income bracket. The odds of Black Friday shopping is
$e^{-0.342} = 0.710$
We can use our predicted probability plot to estimate the probability of certain
individuals going shopping. For example, the predicted probability of an 
individual between 45-59 years old with a household income of $100,000+ shopping
early is 0.159, so about 15.9 %. The predicted probability of going Black Friday
shopping early for an individual aged 15-29 years old with a household income of
$0 to $24,999 is 0.415, so about 41.5 %.

**Coefficients Interpretation:**

- Holding age constant, for someone in the $25,000 to 74,999 income bracket, we
expect log-odds of Black Friday shopping to decrease by 0.234. That is,
the odds of Black Friday shopping is expected to be multiplied by  
$e^{-0.234} = 0.791$

- Similarly holding age constant, for someone in the $75,000 to 99,999 income 
bracket, we expect log-odds of Black Friday shopping to decrease by 0.472. That 
is, the odds of Black Friday shopping is expected to be multiplied by 
$e^{-0.472} = 0.6237$. 

- And for someone in the $100,000 income bracket, we expect log-odds of Black 
Friday shopping to decrease by 0.719 and  odds of Black Friday shopping is 
expected to be multiplied by $e^{-0.719} = 0.487$. 

- Holding Income constant for someone in the 30-44 year old age bracket, we
expect log-odds of Black Friday shopping to decrease by 0.161. That is,
the odds of Black Friday shopping is expected to be multiplied by 
$e^{-0.161} = 0.851$. 

- Holding Income constant for someone in the 45-59 year old age bracket, we
expect log-odds of Black Friday shopping to decrease by 0.606. That is,
the odds of Black Friday shopping is expected to be multiplied by 
$e^{-0.546} = 0.546$. 

- Finally, holding Income constant for someone in the 60+ year old age bracket, 
we expect log-odds of Black Friday shopping to decrease by 1.054. That is,
the odds of Black Friday shopping is expected to be multiplied by 
$e^{-1.054} = 0.349$. 

**How we arrived at our answer**
We arrived at our best fit model by eliminating variables based on whether they 
had a high p-value or not, and then analyzing the BIC scores for the three 
logistic regression models we made. We found that our final model had the lowest
BIC value, and concluded that it had the best model performance while not being 
overly complex. 
To perform this backwards elimination, we started out including each relevant 
variable in our logistic model that we thought offered an interesting 
statistical analysis. From this 
technique, we decided to first eliminate gender, as the coefficient gender had a
high p-value of 0.307. This is also shown in our initial exploratory data 
analysis, as you can see that gender did not have that much of an effect on 
whether an individual went Black Friday shopping early. That is, both males and 
females had about the same percentage of the sex that said they would go Black 
Friday shopping. After eliminating gender, we created a new logistic regression 
model. From this next model, we decided to eliminate location_type, as it had 
the next highest p-values. Through eliminating the variables that are not 
statistically significant, we ideally found the most suitable model to 
predict the odds of an individual going Black Friday shopping early.
After getting this final model, we analyzed it further by looking at the BIC 
scores, finding that our last model had the lowest one, and the binned 
residuals plot. The low BIC score compared to the other models showed that our 
final model was not overly complex and had the best performance. The results 
from our binned residuals plot, with all over our residuals falling within the 
error bounds, further confirmed that our model was a god fit. Through our 
analysis we could be confident that our logistic regression model with only 
income and age as variables was the best fit in predicting thanksgiving 
shopping.

# Discussion

### Discussion - Summary of what we learned about research question
From our analysis, we learned that age and income are the most relevant 
variables when it comes to determining whether an individual will go Black 
Friday shopping early. We can infer that individuals with a household income 
of $0 - $24,999 and individuals between the age range of 18 to 29 years old are 
the most likely to go Black Friday shopping on Thanksgiving.
Our research question was what is the relationship between household income, 
age, gender, and location type with likelihood that someone will go Black Friday
shopping on Thanksgiving? While our initial hypothesis was that as income 
increases a greater percentage of individuals will shop, our results showed that
the exact opposite was the case. We learned that age and household income are 
the most relevant variables, as there was a relationship for age (as age 
increases, shopping probability decreases) and income (as income increases, 
shopping probability decreases) but not much of a difference between male’s and 
female’s likelihood of shopping or between individuals in urban vs rural or 
suburban areas. 

**Data explanation:**
As household income increases, individuals will not necessarily care as much 
about sales or require them to purchase things, and therefore will be less 
likely to rush to stores early for lower prices, so the income trend makes 
sense. Older generations also tend to prefer spending time with their family at 
Thanksgiving dinner, whereas younger generations prefer going out and shopping
so the age trend makes sense. Geographically speaking, there should be more 
stores in urban areas than rural and suburban areas, and culturally speaking, 
shopping tends to be more of a hobby in urban areas than rural and suburban, so 
the (barely) greater likelihood of urban residents shopping early makes sense. 
Overall, the percentages of individuals saying yes to going Black Friday 
shopping on Thanksgiving was fairly low in 2015, which could be explained by the
surge of shopping becoming more heavily online due to Cyber Monday sales.

**Limitations: Critiquing our Methods**
While our use of eliminating values based on p-values and finding the model with
the lowest BIC showed that there was some improvement with our respective models
as we narrowed the relevant variables down to age and income, none of the 
changes were incredibly drastic to say that one was exceptionally  better than 
the others. We found that comparatively, our third seemed like it was slightly 
better than the others. 

When looking back at our methods, using logistic 
regression comes with assumptions of independence and linearity in the log-odds.
However, our data may violate the independence assumption since we’re analyzing 
survey data which is not the most random sample and is subject to bias from 
optional response. So, there could be some reason to say that the data points 
were correlated since it was not entirely random. There are also issues with the
reliability and validity of our data, as it was gathered from a survey. The 
survey responses may not be fully reliable as they are subject to opinion bias. 
Many of the survey questions were asking about the respondents opinion (i.e How 
would you describe where you live?) so it was mainly just based on what they 
thought and could not be entirely valid or reliable. In terms of linearity, an 
issue may arise if the predictors are correlated, such as if location has to do 
with household income, which would lead to the coefficient estimates being 
unreliable. 

There may be further shortfalls in our methodology with our usage of
BIC. With BIC, the approximation is only valid for a sample size that is the 
number of data points larger than the number of parameters in the model and BIC 
cannot handle models complex in variable selection. Additionally, because  BIC 
penalizes for complexity more heavily, the low score for our third, and least 
complex model, could also be attributed to it having less variables than our 
first and second models.

We did not look at the pseudo R squared value generated by model performance
for out logistic regression models as we decided it was not a very useful
or appropriate metric in our case. Additionally, because it is not adjusted R 
squared, this value increases with additional variables, and is not a good
measure of the fit of our models.

*What we would do differently:*
So, if we were to start over with the project and wanted to use more variables, 
We could extend to  methods beyond BIC and looking at the p-values of variables 
to analyze our logistic regression model. In terms of independence, these 
critiques are simply based on the data set that we found so we could possibly 
bring in other datasets that have more info. For thinking about the further 
shortfalls of our model and where we could take the model further, we could also
look at interaction effects and include more variables. Overall, there is 
evidently a lot more that goes into whether an individual would go Black Friday 
shopping early on Thanksgiving day or not beyond the ones we had access to in 
this set which could pose for interesting statistical analysis in the future. 